Assessing the Global COVID19 Impact on Air Transport with Open Data

### 2021-06-09 paper.Rmd
It worked!! TinyTex fixed!

<!--| 3. Purpose and significance of the paper.  -->
This paper approaches the impact of the pandemic as a massive service disruption of the pre-pandemic global connectivity and regional air transport networks. In particular, the project aims to provide data analytical evidence for policy success and transformation of the air transportation system. As an aspirational goal, the industry aims to recover in a “greener” manner. To date, no assessment of this transformational aspects has been conducted.

@@

* data-analytical approach - using open data / freely available (tbd: validated against organisational data)
* ...

>>>>

<!--| 3. Purpose and significance of the paper.  -->

This paper approaches the impact of the pandemic as a massive service disruption of the pre-pandemic global connectivity and regional air transport networks. In particular, the project aims to provide data analytical evidence for policy success and transformation of the air transportation system. As an aspirational goal, the industry aims to recover in a "greener" manner. To date, no assessment of this transformational aspects has been conducted.

@@

-   data-analytical approach - using open data / freely available (tbd: validated against organisational data)
-   ...

### 2021-06-09 paper.tex
It worked!! TinyTex fixed!

%% ---- classic IEEETrans one column per institution --------
 %% -- beg if/affiliation.institution-columnar
\IEEEauthorblockN{
  %% -- beg for/affiliation.institution.author
Rainer Koelle %% -- end for/affiliation.institution.author
}
\IEEEauthorblockA{Performance Review Unit\\
EUROCONTROL\\
Brussels (Belgium)
  %% -- beg for/affiliation.institution.author
\\rainer.koelle@eurocontrol.int
 %% -- end for/affiliation.institution.author
}
\and
\IEEEauthorblockN{
  %% -- beg for/affiliation.institution.author
Fabio Coneiro Barbarosa %% -- end for/affiliation.institution.author
}
\IEEEauthorblockA{tbd \ldots{}\\
DECEA\\
tbd location - suggest Rio (Brazil)
  %% -- beg for/affiliation.institution.author
\\second\_author@somedomain.com
 %% -- end for/affiliation.institution.author
}
 %% -- end for/affiliation.institution
 %% -- end if/affiliation.institution-columnar
%% ----------------------------------------------------------

>>>>

%% ---- classic IEEETrans one column per institution --------
 %% -- beg if/affiliation.institution-columnar
\IEEEauthorblockN{
  %% -- beg for/affiliation.institution.author
Rainer Koelle %% -- end for/affiliation.institution.author
}
\IEEEauthorblockA{Performance Review Unit\\
EUROCONTROL\\
Brussels (Belgium)
  %% -- beg for/affiliation.institution.author
\\rainer.koelle@eurocontrol.int
 %% -- end for/affiliation.institution.author
}
\and
\IEEEauthorblockN{
  %% -- beg for/affiliation.institution.author
Fabio Lourenco Carneiro Barbosa %% -- end for/affiliation.institution.author
}
\IEEEauthorblockA{Subdepartment of Operations\\
DECEA\\
Rio de Janeiro (Brazil)
  %% -- beg for/affiliation.institution.author
\\barbosaflcb@fab.mil.br
 %% -- end for/affiliation.institution.author
}
 %% -- end for/affiliation.institution
 %% -- end if/affiliation.institution-columnar
%% ----------------------------------------------------------
